Spfy: applying a graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-01-19 paper-webserver.tex
ADD: example table
ADD: trimmed table

\usepackage[parfill]{parskip}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
% Author
\usepackage{authblk}
% Images
\usepackage{graphicx}
% \usepackage{svg}

@@

\section{RESULTS}
Spfy was tested with 4,622 public \textit{E. coli} assembled genomes from Enterobase, storing every sequence and results for all included analysis modules.
Spfy provides real-time subtyping, and the results are immediately displayed to the user following their completion.
Subtyping options include O-antigen, H-antigen, Shiga-toxin 1, Shiga-toxin 2, and Intimin typing. Reference-lab tests include virulence factor and anti-microbial resistance annotation. All genomes are analyzed within the pan-genome framework of \textit{E. coli}, and results from all analyses are automatically associated with the source genome.
The resulting database had 1,333 nodes and 683,666 leaves, with 374,836,872 object properties. \par

@@

>>>>

\usepackage[parfill]{parskip}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
% Author
\usepackage{authblk}
% Images
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{longtable}
% \usepackage{svg}

@@

\section{RESULTS}
Spfy was tested with 10,243 public \textit{E. coli} assembled genomes from Enterobase, storing every sequence and results for all included analysis modules.
Spfy provides real-time subtyping, and the results are immediately displayed to the user following their completion.
Subtyping options include O-antigen, H-antigen, Shiga-toxin 1, Shiga-toxin 2, and Intimin typing. Reference-lab tests include virulence factor and anti-microbial resistance annotation. All genomes are analyzed within the pan-genome framework of \textit{E. coli}, and results from all analyses are automatically associated with the source genome.
The resulting database had 17,820 nodes and 3,811,473 leaves, with 1,125,909,074 object properties. \par

\small \input{tables/database}

@@

\section{APPENDIX}
